Preliminary Survey on Statistics and Software

### 2019-09-06 content/assignment/00-preliminary-survey.Rmd
Add links to survey answers (testing icons)

- [<i class="fas fa-file-pdf"></i> `Download as PDF`](/homeworks/00-preliminary-survey.pdf)

>>>>

- [<i class="fas fa-file-pdf"></i> `Download as PDF`](/homeworks/00-preliminary-survey.pdf)
- [<i class="far fa-life-ring"></i><i class="fas fa-file-pdf"></i> `Answer Key`](/homeworks/00-preliminary-survey-answers.html)
- [<i class="far fa-life-ring"></i><i class="fas fa-external-link-square-alt"></i> `Answer Key`](/homeworks/00-preliminary-survey-answers.pdf)
